---
title: "make_Indianapolis_sfnetwork"
author: "Daniel P. Riggins"
output: html_document
---

```{r}
library(sf)
library(sfnetworks)
library(tidyverse)
library(mapview)
```

We'll start with downloading the data and then follow along with the `sfnetwork` package's "Network pre-processing and cleaning" vignette.

```{r}
Indy_streets <- st_read("https://opendata.arcgis.com/datasets/fa9ec663cf25407a9b7645ff14334a7f_13.geojson") 

Indiana_ave_streets <- Indy_streets %>%
    # Crop to Indiana Ave District
    st_crop(c(xmin = -86.189233, ymin = 39.770670, xmax = -86.160613, ymax = 39.789350)) %>%
    # Convert all geometries to MULTILINESTRINGS
    st_cast("MULTILINESTRING") %>%
    # Convertt all geomeries to LINESTRING
    st_cast("LINESTRING") %>%
    # Convert to network object
    as_sfnetwork()

Indiana_ave_streets
```

```{r}
edges <- Indiana_ave_streets %>%
    activate("edges") %>%
    st_as_sf()

nodes <- Indiana_ave_streets %>%
    activate("nodes") %>%
    st_as_sf()

mapview(nodes, col.regions = "darkred", legend = NULL) + 
  mapview(edges, color = "black", lwd = 2, legend = NULL)
```

## Common pre-processing tasks

### Rounding coordinates

Not necessary in this dataset

### Dealing with one-way edges

Working on this. See [github discussion](https://github.com/luukvdmeer/sfnetworks/discussions/145).

## Network cleaning functions

### Simplify network

Not desired in this dataset.

### Subdivide edges

Not necessary when inspecting the dataset on mapview above.

### Smooth pseudo nodes

```{r}
smoothed <- tidygraph::convert(Indiana_ave_streets, to_spatial_smooth)

smoothed
```
```{r}
smooth_edges <- smoothed %>%
    activate("edges") %>%
    st_as_sf()

smooth_nodes <- smoothed %>%
    activate("nodes") %>%
    st_as_sf()

mapview(smooth_nodes, col.regions = "darkred", legend = NULL) + 
  mapview(smooth_edges, color = "black", lwd = 2, legend = NULL)
```


